\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-23 doc/sw-system.tex
Short speed section done. Closes #107

% How fast does the \sw crowd classify subjects? Each agent records the
% timestamp of each classification its volunteer makes; by measuring the time
% lags between successive classifications we can make estimates of each
% volunteer's speed, and that of the crowd.
%
% A histogram of all time lags for all volunteers is shown in
% \Fref{fig:crowd:timelags}, with those of the ``experienced volunteers''
% (those who classified 10 or more training subjects.) overlaid.
%
% \todo{PJM}{Make this histogram, and try and infer the typical inter-session
% lag.}
%
% Defining a new classification session to have started at least X minutes since
% the previous classification, we assign all classifications into sessions, and
% compute the mean intra-session time lag recorded by each agent. This gives
% some measure of classification speed within a session; we also compute the
% mean session length, and the rate of information contribution. The
% latter is the most relevant measure of speed for future project design. The
% distributions of these speeds are shown in \Fref{fig:crowd:speeddists}, in a corner
% plot that also shows the effort and skill from \Fref{fig:crowd:cornerplot}. We
% see that ...

The overall contribution rate for the \sw crowd was found,
and is plotted as a function of time in \Fref{fig:crowd:speed}. We see that
...

\todo{Phil, Chris}{Compute classification speeds, make plots, discuss. \#95}

>>>>

How fast does the \sw crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both Stage 1 and Stage
2 in \Fref{fig:results:speed}, normalizing the speed and time axes to the
respective totals. The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size. Stage 1 (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users). The asymptotic classification rate was $\sim10^3$ per hour. The average skill was found to be approximately constant over the lifetime of Stage 1, leading to a contribution rate that tracks closely the classification rate. (A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) Stage 2 (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=\linewidth]{sw-system-figs/rate_classification.png}
\caption{Fractional classification rate in the \SW CFHTLS survey.}
\label{fig:results:speed}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The similarities between Stage 1 and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy). For example, the completion time for a \SW project could be approximated as
\begin{equation}
    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
                               \left(\frac{N_s}{10^4}\right),
\end{equation}
where $N_s$ is the number of subjects to be classified, and $N_p$ is the number of volunteers in the crowd.
